Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/related.tex
Update on Overleaf.

The related work on array languages, compilers, libraries, and frameworks, both for dense and structured computation, spans several areas.

%% Libraries: Numpy, blas, graphblas, SplAtt, Scipy
%% Languages: Halide, Lift, TVM, OptiML
%% Languages: Lgen/Spiral, LAMapping system,
%% languages sparse: TVM Sparse, Tiachi, SPF, TACO, Stut, various extensiosn to TACO,
%% SQL: HyPer, SDQL + Formats, Vectorwise, Morphesu,

%% Most similar to us: SDQL

>>>>

The related work on array languages and libraries, both for dense and structured computation, spans several areas.
%
We highlight these works based on if they are a library or language vs. if they are dense or more general.

\paragraph{Dense Libraries:}

\paragraph{Structured Libraries:}

\paragraph{Dense Tensor Compilers:}

\paragraph{Tensor Compilers for Structured Data:}

%% Libraries: Numpy, LAPACK, blas, graphblas, SplAtt, Scipy, Petsc, 
%% Languages: Halide, Lift, TVM, OptiML
%% Languages: Lgen/Spiral, LAMapping system,
%% languages sparse: TVM Sparse, Tiachi, SPF, TACO, Stut, various extensiosn to TACO,
%% SQL: HyPer, SDQL + Formats, Vectorwise, Morphesu,

%% Most similar to us: SDQL, SPF Leader Follower, Taichi
